\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-26 paper.tex
all updated

\textbf{Evaluation results.}

Figure \ref{availability_fig1} compares, under different demand arrival rates, 
the admission results of $\mathsf{BATE}$  against  
the optimal strategy and the \textit{fixed} one, i.e., step (1) in $\mathsf{BATE}$. 
Figure \ref{availability_fig1}(a) shows that, $\mathsf{BATE}$ falsely rejects at most 4\% demands (using the optimal solution as a baseline), but accepts up to 50\% more demands with a much smaller variance than Fixed. 
It can also utilize at least 10\% higher bandwith than Fixed, as shown in Figure \ref{availability_fig1}(b). 
We also qualify their efficiency by measuring the admission control delay, and Figure \ref{availability_fig1}(c) demonstrates that, $\mathsf{BATE}$ runs at least 30$\times$ faster than directly solving the MILP optimization problem, and always finishes within 1 second. 
%
%\begin{figure}[t]
%\begin{center}
%\includegraphics [width=0.8\columnwidth] {fig/evaluation/sim-monney.pdf}
%\caption{Profit gain after failures}
%\label{sim-profit}
%\end{center}
%\end{figure}

@@

Finally, we compute the approximation ratio of our greedy failure recovery algorithm, 
which is defined as dividing the optimal profit by the profit achieved. 
Figure \ref{approximation} shows that, 
our 2-approximation algorithm achieves a ratio between 1 and 1.25 in real scenarios, 
and the average profit loss is around 10\%. 
This comes with a speedup by at least 100$\times$ under normal load (rate=6). 
 (more details can be seen in Appendix \ref{testbed-appendix}).
%Satisfaction percentage. It denotes the percentages of applications whose achieved availability is larger than the corresponding target.
%Figure \ref{availability_fig1}(b) shows 
%$\mathsf{BATE}$ performs about 20\%, 25\%, 30\%,  40\% better than TEAVAR, SMORE, SWAN, FFC, respectively.
%%Specially, when traffic scale is 3, more than 70\% applications can satisfy their availability demands, which is at least 30\% better than TEAVAR.
%Specially, the advantage of $\mathsf{BATE}$  is more obvious when there are resource competition (e.g., $s=3$).
%%The reason for this is that $\mathsf{BATE}$ considers the bandwidth-based availability demand differentiation of applications.
%This picture also demonstrates that the performance of $\mathsf{BATE}$ doesn't depend on particular network topology and traffic.
%Next, we take IBM trace as the example and perform the experiments.

>>>>

\textbf{Evaluation results.}
Figure \ref{availability_fig1} compares, under different demand arrival rates, 
the admission results of $\mathsf{BATE}$  against  
the optimal strategy and the \textit{fixed} one, i.e., step (1) in $\mathsf{BATE}$. 
Figure \ref{availability_fig1}(a) shows that, $\mathsf{BATE}$ falsely rejects at most 4\% demands (using the optimal solution as a baseline), but accepts up to 50\% more demands with a much smaller variance than Fixed. 
It can also utilize at least 10\% higher bandwith than Fixed, as shown in Figure \ref{availability_fig1}(b). 
We also qualify their efficiency by measuring the admission control delay, and Figure \ref{availability_fig1}(c) demonstrates that, $\mathsf{BATE}$ runs at least 30$\times$ faster than directly solving the MILP optimization problem, and always finishes within 1 second. 
%
%\begin{figure}[t]
%\begin{center}
%\includegraphics [width=0.8\columnwidth] {fig/evaluation/sim-monney.pdf}
%\caption{Profit gain after failures}
%\label{sim-profit}
%\end{center}
%\end{figure}

@@

Finally, we compute the approximation ratio of our greedy failure recovery algorithm, 
which is defined as dividing the optimal profit by the profit achieved. 
Figure \ref{approximation} shows that, 
our 2-approximation algorithm achieves a ratio between 1 and 1.25 in real scenarios, 
and the average profit loss is around 10\%. 
This comes with a speedup by at least 100$\times$ under normal load (rate=6). 
Due to space limitations, its details are put in Appendix \ref{testbed-appendix}.
%Satisfaction percentage. It denotes the percentages of applications whose achieved availability is larger than the corresponding target.
%Figure \ref{availability_fig1}(b) shows 
%$\mathsf{BATE}$ performs about 20\%, 25\%, 30\%,  40\% better than TEAVAR, SMORE, SWAN, FFC, respectively.
%%Specially, when traffic scale is 3, more than 70\% applications can satisfy their availability demands, which is at least 30\% better than TEAVAR.
%Specially, the advantage of $\mathsf{BATE}$  is more obvious when there are resource competition (e.g., $s=3$).
%%The reason for this is that $\mathsf{BATE}$ considers the bandwidth-based availability demand differentiation of applications.
%This picture also demonstrates that the performance of $\mathsf{BATE}$ doesn't depend on particular network topology and traffic.
%Next, we take IBM trace as the example and perform the experiments.
